Optimization of String Rewriting Operations for 3D Fractal Generation with Genetic Algorithms

### 2018-06-02 Optimization-of-String-Rewriting-Operations-for-3D-Fractal-Generation-with-Genetic-Algorithms/paper.tex
Small amount of text was added.
Addition of small amout of text.

>>>>

A finite 3D space is represented as three-dimensional array of voxels in the model. Each voxel is encoded with a single long integer value, which consists of the RGB information for the color of the voxel. In this model 32 different transition 3x3x3 matrices are selected, each corresponding to the one of the 32 colors.
